The problem and promise of scale in multilayer networks

### 2019-09-11 paper/introduction.Rmd
more intro

# Multilayer Networks

Multilayer networks combine multiple networks layers with interlayer edges

@@

What kinds of ML nets exist

@@

# Scale
Scale

in grain and extent

grain is this

extent is this

>>>>

# Multilayer Networks
Multilayer networks combine network layers with interlayer edges

Two main types of multilayer networks exist: multiplex networks and interconnected networks. Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks). Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks).

Of these, we have identified multirelational networks, networks of networks, intercontextual networks and spatial networks as likely to have spatial and scale considerations

@@

@@

# Scale
What is scale

in LE lit, how has scale been investigated

Elements of scale relevant to animal social systems, animal movement data, landcover data

Grain is this, extent is this

How might scale influence results

What kinds of spatial scale are there
